---
title: "anova_soil_properties_donors_mixtures"
output: html_document
date: "2025-02-10"
---

library
```{r}
library(agricolae)
library("car")
```


Input data
```{r}
chemistry = read.csv("./soil_properties_controls_mixtures.csv", header = T)
chemistry = data.frame(chemistry)
```

Ph
```{r}
head(chemistry)
anova_pH <- aov(data = chemistry, pH ~ soil)
anova_pH
summary(anova_pH)

#Normality - shapiro-wilk's test
qqPlot(anova_pH$residuals) #Plot
shapiro.test(anova_pH$residuals)
#Homogenity test
bartlett.test(pH ~ soil, data = chemistry)
leveneTest(pH ~ soil, data = chemistry)

summary(anova_pH)
TukeyHSD(anova_pH, conf.level = 0.95)

pH.hsd <- HSD.test(anova_pH, "soil", group=TRUE)
pH.hsd
```
Phosphorus
```{r}
anova_phos <- aov(data = chemistry, Phosphorus ~ soil)
anova_phos
summary(anova_phos)
#Normality - shapiro-wilk's test
qqPlot(anova_phos$residuals)
shapiro.test(anova_phos$residuals)
#Homogenity test
bartlett.test(log(Phosphorus) ~ soil, data = chemistry)
leveneTest(Phosphorus ~ soil, data = chemistry)

summary(anova_phos)
TukeyHSD(anova_phos, conf.level = 0.95)
phos.hsd <- HSD.test(anova_phos, "soil", group=TRUE)
phos.hsd
```
Potassium
```{r}
anova_potassium <- aov(data = chemistry, Potassium ~ soil)
anova_potassium
summary(anova_potassium)
#Normality - shapiro-wilk's test
qqPlot(anova_potassium$residuals)
shapiro.test(anova_potassium$residuals)
#Homogenity test
bartlett.test(log(Potassium) ~ soil, data = chemistry)
leveneTest(Potassium ~ soil, data = chemistry)

summary(anova_potassium)
TukeyHSD(anova_potassium, conf.level = 0.95)
potassium.hsd <- HSD.test(anova_potassium, "soil", group=TRUE)
potassium.hsd

```
Magnesium
```{r}
anova_mg <- aov(data = chemistry, Magnesium ~ soil)
anova_mg
summary(anova_mg)
#Normality - shapiro-wilk's test
qqPlot(anova_mg$residuals)
shapiro.test(anova_mg$residuals)
#Homogenity test
#bartlett.test(Magnesium ~ soil, data = chemistry)
leveneTest(Magnesium ~ soil, data = chemistry)

summary(anova_mg)
TukeyHSD(anova_mg, conf.level = 0.95)
mg.hsd <- HSD.test(anova_mg, "soil", group=TRUE)
mg.hsd
```
Calcium
```{r}
anova_ca <- aov(data = chemistry, Calcium ~ soil)
anova_ca
summary(anova_ca)
#Normality - shapiro-wilk's test
qqPlot(anova_ca$residuals)
shapiro.test(anova_ca$residuals)
#Homogenity test
bartlett.test(Calcium ~ soil, data = chemistry)
leveneTest(Calcium ~ soil, data = chemistry)

summary(anova_ca)
TukeyHSD(anova_ca, conf.level = 0.95)
ca.hsd <- HSD.test(anova_ca, "soil", group=TRUE)
ca.hsd
```
Acidity index
```{r}
anova_acidity_index <- aov(data = chemistry, log(Acidity_index) ~ soil)
anova_acidity_index
summary(anova_acidity_index)
#Normality - shapiro-wilk's test
qqPlot(anova_acidity_index$residuals)
shapiro.test(anova_acidity_index$residuals)
#Homogenity test
#bartlett.test(Acidity_index ~ soil, data = chemistry)
leveneTest(Acidity_index~ soil, data = chemistry)

summary(anova_acidity_index)
TukeyHSD(anova_acidity_index, conf.level = 0.95)
acidity_index.hsd <- HSD.test(anova_acidity_index, "soil", group=TRUE)
acidity_index.hsd
```
CEC
```{r}
anova_cec <- aov(data = chemistry, CEC ~ soil)
anova_cec
summary(anova_cec)
#Normality - shapiro-wilk's test
qqPlot(anova_cec$residuals)
shapiro.test(anova_cec$residuals)
#Homogenity test
bartlett.test(CEC ~ soil, data = chemistry)
#leveneTest(CEC ~ soil, data = chemistry)

summary(anova_cec)
TukeyHSD(anova_cec, conf.level = 0.95)
cec.hsd <- HSD.test(anova_cec, "soil", group=TRUE)
cec.hsd
```
K percent saturation
```{r}
anova_K_sat_cec <- aov(data = chemistry, K_percent_saturation_of_CEC ~ soil)
anova_K_sat_cec
summary(anova_K_sat_cec)
#Normality - shapiro-wilk's test
qqPlot(anova_K_sat_cec$residuals)
shapiro.test(anova_K_sat_cec$residuals)
#Homogenity test
#bartlett.test(Magnesium ~ soil, data = chemistry)
leveneTest(K_percent_saturation_of_CEC ~ soil, data = chemistry)

summary(anova_K_sat_cec)
TukeyHSD(anova_K_sat_cec, conf.level = 0.95)
K_sat_cec.hsd <- HSD.test(anova_K_sat_cec, "soil", group=TRUE)
K_sat_cec.hsd
```
Mg percent saturation of CEC
```{r}
anova_Mg_sat_cec <- aov(data = chemistry, Mg_percent_saturation_of_CEC ~ soil)
anova_Mg_sat_cec
summary(anova_Mg_sat_cec)
#Normality - shapiro-wilk's test
qqPlot(anova_Mg_sat_cec$residuals)
shapiro.test(anova_Mg_sat_cec$residuals)
#Homogenity test
bartlett.test(Mg_percent_saturation_of_CEC ~ soil, data = chemistry)
#leveneTest(Mg_percent_saturation_of_CEC ~ soil, data = chemistry)

summary(anova_Mg_sat_cec)
TukeyHSD(anova_Mg_sat_cec, conf.level = 0.95)
Mg_sat_cec.hsd <- HSD.test(anova_Mg_sat_cec, "soil", group=TRUE)
Mg_sat_cec.hsd
```
Ca percent saturation
```{r}
anova_Ca_sat_cec <- aov(data = chemistry, Ca_percent_saturation_of_CEC ~ soil)
anova_Ca_sat_cec
summary(anova_Ca_sat_cec)
#Normality - shapiro-wilk's test
qqPlot(anova_Ca_sat_cec$residuals)
shapiro.test(anova_Ca_sat_cec$residuals)
#Homogenity test
bartlett.test(Ca_percent_saturation_of_CEC ~ soil, data = chemistry)
leveneTest(Ca_percent_saturation_of_CEC ~ soil, data = chemistry)

summary(anova_Ca_sat_cec)
TukeyHSD(anova_Ca_sat_cec, conf.level = 0.95)

Ca_sat_cec.hsd <- HSD.test(anova_Ca_sat_cec, "soil", group=TRUE)
Ca_sat_cec.hsd
```
Zinc
```{r}
anova_zinc <- aov(data = chemistry, Zinc ~ soil)
anova_zinc
summary(anova_zinc)
#Normality - shapiro-wilk's test
qqPlot(anova_zinc$residuals)
shapiro.test(anova_zinc$residuals)
#Homogenity test
bartlett.test(Zinc ~ soil, data = chemistry)
leveneTest(log(Zinc) ~ soil, data = chemistry)

summary(anova_zinc)
TukeyHSD(anova_zinc, conf.level = 0.95)

zinc.hsd <- HSD.test(anova_zinc, "soil", group=TRUE)
zinc.hsd
```
Copper 
```{r}
anova_copper <- aov(data = chemistry, Copper ~ soil)
anova_copper
summary(anova_copper)
#Normality - shapiro-wilk's test
qqPlot(anova_copper$residuals)
shapiro.test(anova_copper$residuals)
#Homogenity test
bartlett.test(Copper ~ soil, data = chemistry)
leveneTest(Copper ~ soil, data = chemistry)

summary(anova_copper)
TukeyHSD(anova_copper, conf.level = 0.95)
copper.hsd <- HSD.test(anova_copper, "soil", group=TRUE)
copper.hsd
```
Sulfur
```{r}
anova_sulfur <- aov(data = chemistry, Sulfur ~ soil)
anova_sulfur
summary(anova_sulfur)
#Normality - shapiro-wilk's test
qqPlot(anova_sulfur$residuals)
shapiro.test(anova_sulfur$residuals)
#Homogenity test
bartlett.test(Sulfur ~ soil, data = chemistry)
#leveneTest(Sulfur ~ soil, data = chemistry)

summary(anova_sulfur)
TukeyHSD(anova_sulfur, conf.level = 0.95)
sulfur.hsd <- HSD.test(anova_sulfur, "soil", group=TRUE)
sulfur.hsd
```
Percent OM
```{r}
anova_OM <- aov(data = chemistry, Percent_Organic_Matter ~ soil)
anova_OM
summary(anova_OM)
#Normality - shapiro-wilk's test
qqPlot(anova_OM$residuals)
shapiro.test(anova_OM$residuals)
#Homogenity test
bartlett.test(Percent_Organic_Matter ~ soil, data = chemistry)
leveneTest(Percent_Organic_Matter ~ soil, data = chemistry)

summary(anova_OM)
TukeyHSD(anova_OM, conf.level = 0.95)
OM.hsd <- HSD.test(anova_OM, "soil", group=TRUE)
OM.hsd
```
Nitrate nitrogen
```{r}
anova_nitrate <- aov(data = chemistry, log(Nitrate_nitrogen) ~ soil)
anova_nitrate
summary(anova_nitrate)
#Normality - shapiro-wilk's test
qqPlot(anova_nitrate$residuals) 
shapiro.test(anova_nitrate$residuals)
#Homogenity test
bartlett.test(log(Nitrate_nitrogen) ~ soil, data = chemistry)
leveneTest(Percent_Organic_Matter ~ soil, data = chemistry)

summary(anova_nitrate)
TukeyHSD(anova_nitrate, conf.level = 0.95)
nitrate.hsd <- HSD.test(anova_nitrate, "soil", group=TRUE)
nitrate.hsd
```
Soluble salts 
```{r}
anova_sol_salts <- aov(data = chemistry, log(Soluble_Salts) ~ soil)
anova_sol_salts
summary(anova_sol_salts)

#Normality - shapiro-wilk's test
qqPlot(anova_sol_salts$residuals)
shapiro.test(anova_sol_salts$residuals)
#Homogenity test
bartlett.test(log(Soluble_Salts) ~ soil, data = chemistry)
leveneTest(log(Soluble_Salts) ~ soil, data = chemistry)

summary(anova_sol_salts)
TukeyHSD(anova_sol_salts, conf.level = 0.95)
sol_salts.hsd <- HSD.test(anova_sol_salts, "soil", group=TRUE)
sol_salts.hsd

```
Ammonium nitrogen
```{r}
anova_ammonium <- aov(data = chemistry, Ammonium_nitrogen ~ soil)
anova_ammonium
summary(anova_ammonium)
#Normality - shapiro-wilk's test
qqPlot(anova_ammonium$residuals)
shapiro.test(anova_ammonium$residuals)
#Homogenity test
bartlett.test(Ammonium_nitrogen ~ soil, data = chemistry)
leveneTest(log(Soluble_Salts) ~ soil, data = chemistry)

summary(anova_ammonium)
TukeyHSD(anova_ammonium, conf.level = 0.95)

ammonium.hsd <- HSD.test(anova_ammonium, "soil", group=TRUE)
ammonium.hsd

```
Total N percent
```{r}
anova_total_N <- aov(data = chemistry, log(Total_N_Percent) ~ soil)
anova_total_N
summary(anova_total_N)

#Normality - shapiro-wilk's test
qqPlot(anova_total_N$residuals)
shapiro.test(anova_total_N$residuals)
#Homogenity test
bartlett.test(Total_N_Percent ~ soil, data = chemistry)
leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_total_N)
TukeyHSD(anova_total_N, conf.level = 0.95)
totalN.hsd <- HSD.test(anova_total_N, "soil", group=TRUE)
totalN.hsd
```
Total C percent 
```{r}
anova_total_C <- aov(data = chemistry, Total_C_percent ~ soil)
anova_total_C
summary(anova_total_C)
#Normality - shapiro-wilk's test
qqPlot(anova_total_C$residuals)
shapiro.test(anova_total_C$residuals)
#Homogenity test
bartlett.test(Total_C_percent ~ soil, data = chemistry)
leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_total_C)
TukeyHSD(anova_total_C, conf.level = 0.95)
totalC.hsd <- HSD.test(anova_total_C, "soil", group=TRUE)
totalC.hsd
```
Sand percent
```{r}
anova_sand <- aov(data = chemistry, Sand_percent ~ soil)
anova_sand
summary(anova_sand)
#Normality - shapiro-wilk's test
qqPlot(anova_sand$residuals)
shapiro.test(anova_sand$residuals)
#Homogenity test
bartlett.test(Sand_percent ~ soil, data = chemistry)
#leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_sand)
TukeyHSD(anova_sand, conf.level = 0.95)

sand.hsd <- HSD.test(anova_sand, "soil", group=TRUE)
sand.hsd

```
Silt percent
```{r}
anova_silt <- aov(data = chemistry, Silt_percent ~ soil)
anova_silt
summary(anova_silt)
shapiro.test(anova_silt$residuals)
#Normality - shapiro-wilk's test
qqPlot(anova_silt$residuals)
shapiro.test(anova_silt$residuals)
#Homogenity test
bartlett.test(Silt_percent ~ soil, data = chemistry)
leveneTest(Silt_percent ~ soil, data = chemistry)

summary(anova_silt)
TukeyHSD(anova_silt, conf.level = 0.95)
silt.hsd <- HSD.test(anova_silt, "soil", group=TRUE)
silt.hsd

```
Clay percent
```{r}
anova_clay <- aov(data = chemistry, Clay_percent ~ soil)
anova_clay
summary(anova_clay)
#Normality - shapiro-wilk's test
qqPlot(anova_clay$residuals)
shapiro.test(anova_clay$residuals)
#Homogenity test
bartlett.test(Clay_percent ~ soil, data = chemistry)
#leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_clay)
TukeyHSD(anova_clay, conf.level = 0.95)

clay.hsd <- HSD.test(anova_clay, "soil", group=TRUE)
clay.hsd
```
Gravel percent retained
```{r}
anova_gravel_retained <- aov(data = chemistry, Gravel_percent_Retained ~ soil)
anova_gravel_retained
summary(anova_gravel_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_gravel_retained$residuals)
shapiro.test(anova_gravel_retained$residuals)
#Homogenity test
bartlett.test(Gravel_percent_Retained ~ soil, data = chemistry)
leveneTest(Gravel_percent_Retained ~ soil, data = chemistry)

summary(anova_gravel_retained)
TukeyHSD(anova_gravel_retained, conf.level = 0.95)

shapiro.test(anova_gravel_retained$residuals)

anova_gravel_retained.hsd <- HSD.test(anova_gravel_retained, "soil", group=TRUE)
anova_gravel_retained.hsd
```
Very coarse sand percent retained
```{r}
anova_very_coarse_sand_retained <- aov(data = chemistry, Very_Coarse_Sand_percent_Retained ~ soil)
anova_very_coarse_sand_retained
summary(anova_very_coarse_sand_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_very_coarse_sand_retained$residuals)
shapiro.test(anova_very_coarse_sand_retained$residuals)
#Homogenity test
#bartlett.test(log(Very_Coarse_Sand_percent_Retained) ~ soil, data = chemistry)
leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_very_coarse_sand_retained)
TukeyHSD(anova_very_coarse_sand_retained, conf.level = 0.95)

anova_very_coarse_sand_retained.hsd <- HSD.test(anova_very_coarse_sand_retained, "soil", group=TRUE)
anova_very_coarse_sand_retained.hsd

```
Coarse sand percent retained 
```{r}
anova_coarse_sand_retained <- aov(data = chemistry, Coarse_Sand_percent_Retained ~ soil)
anova_coarse_sand_retained
summary(anova_coarse_sand_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_coarse_sand_retained$residuals)
shapiro.test(anova_coarse_sand_retained$residuals)
#Homogenity test
bartlett.test(log(Coarse_Sand_percent_Retained) ~ soil, data = chemistry)
leveneTest(Total_N_Percent ~ soil, data = chemistry)

summary(anova_coarse_sand_retained)
TukeyHSD(anova_coarse_sand_retained, conf.level = 0.95)

anova_coarse_sand_retained.hsd <- HSD.test(anova_coarse_sand_retained, "soil", group=TRUE)
anova_coarse_sand_retained.hsd


```
Medium sand percent retained 
```{r}
anova_med_sand_retained <- aov(data = chemistry, Medium_Sand_percent_Retained ~ soil)
anova_med_sand_retained
summary(anova_med_sand_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_med_sand_retained$residuals)
shapiro.test(anova_med_sand_retained$residuals)
#Homogenity test
bartlett.test(Medium_Sand_percent_Retained ~ soil, data = chemistry)
leveneTest(Medium_Sand_percent_Retained ~ soil, data = chemistry)

summary(anova_med_sand_retained)
TukeyHSD(anova_med_sand_retained, conf.level = 0.95)

anova_med_sand_retained.hsd <- HSD.test(anova_med_sand_retained, "soil", group=TRUE)
anova_med_sand_retained.hsd

```
Fine Sand percent retained
```{r}
anova_fine_sand_retained <- aov(data = chemistry, Fine_Sand_percent_Retained ~ soil)
anova_fine_sand_retained
summary(anova_fine_sand_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_fine_sand_retained$residuals)
shapiro.test(anova_fine_sand_retained$residuals)
#Homogenity test
bartlett.test(log(log(Fine_Sand_percent_Retained)) ~ soil, data = chemistry)
leveneTest(log(log(Fine_Sand_percent_Retained)) ~ soil, data = chemistry)

summary(anova_fine_sand_retained)
TukeyHSD(anova_fine_sand_retained, conf.level = 0.95)

anova_fine_sand_retained.hsd <- HSD.test(anova_fine_sand_retained, "soil", group=TRUE)
anova_fine_sand_retained.hsd

```
VEry fine sand percent retained 
```{r}
anova_very_fine_sand_retained <- aov(data = chemistry, Very_Fine_Sand_percent_Retained ~ soil)
anova_very_fine_sand_retained
summary(anova_very_fine_sand_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_very_fine_sand_retained$residuals)
shapiro.test(anova_very_fine_sand_retained$residuals)
#Homogenity test
bartlett.test(Very_Fine_Sand_percent_Retained ~ soil, data = chemistry)
leveneTest(Very_Fine_Sand_percent_Retained ~ soil, data = chemistry)

summary(anova_very_fine_sand_retained)
TukeyHSD(anova_very_fine_sand_retained, conf.level = 0.95)

anova_very_fine_sand_retained.hsd <- HSD.test(anova_very_fine_sand_retained, "soil", group=TRUE)
anova_very_fine_sand_retained.hsd

```
Fines percent retained
```{r}
anova_fine_retained <- aov(data = chemistry, Fines_percent_Retained ~ soil)
anova_fine_retained
summary(anova_fine_retained)
#Normality - shapiro-wilk's test
qqPlot(anova_fine_retained$residuals)
shapiro.test(anova_fine_retained$residuals)
#Homogenity test
bartlett.test(Fines_percent_Retained ~ soil, data = chemistry)
leveneTest(Fines_percent_Retained ~ soil, data = chemistry)

summary(anova_fine_retained)
TukeyHSD(anova_fine_retained, conf.level = 0.95)

anova_fine_retained.hsd <- HSD.test(anova_fine_retained, "soil", group=TRUE)
anova_fine_retained.hsd

```
